Figures

### 2017-01-15 figures/partnerSIR.tex
tweak diagrams

\newcommand{\instswitchboxes}{
	\node(SS)[bigcompartment]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII]{II};
	\node(pool)[compartment, very thick, above = 10mm of SI, text width = 40mm, align = center, draw = black, top color = white, bottom color = white, dotted]{temporary mixing pool};
}

\newcommand{\pairformboxes}{
        \node(S)[bigcompartment]{S};
        \node(StoI)[right= of S]{};
        \node(I)[bigcompartment,right= of StoI]{I};
	\node(SS)[bigcompartment,below left= of S]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII]{II};
}

>>>>

\newcommand{\instswitchboxes}[1]{
	\node(SS)[bigcompartment, bottom color = #1]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI, bottom color = #1]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII, bottom color = #1]{II};
	\node(pool)[compartment, very thick, above = 10mm of SI, text width = 40mm, align = center, draw = black, bottom color = white, dotted]{temporary mixing pool};
}

\newcommand{\pairformboxes}[1]{
        \node(S)[bigcompartment, bottom color = #1]{S};
        \node(StoI)[right= of S]{};
        \node(I)[bigcompartment,right= of StoI, bottom color = #1]{I};
	\node(SS)[bigcompartment,below left= of S, bottom color = #1]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI, bottom color = #1]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII, bottom color = #1]{II};
}
